\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Journal 10}
\author{Abdullah Abumouzah }

 \usepackage{url}
 
 
\begin{document}

\maketitle

\section{The most significant learning experiences}
\begin{itemize}
    \item First of all I'm so glad I took this class and  I wish I have taken it at the first semester of mine. 
    \item As long as the materials, I think I have good sources out of this class to educate myself when needed specially the videos in YouTube. 
    
    \item Although most of the materials are so informative but I really like how they are organized and how valuable the contents are.  
    \item I've done few independent study and thesis classes as I always needed to read lots of papers, but honestly after taking this class I believe that I wasn't following the right directions and I think I wasted a lot of time just because I wan't doing it the right way.    
    \item One of the valuable skills that I learned from this class is the reading skills and types also when should I conduct each type. That's actually saved me a lot of time because I used to read everything in the paper but now I know what to read and how to read it. 
    \item Working on the survey have taught me a lot. Now it became more obvious what directions should I always follow and what papers should I read and how can I find the most significant information to include into my survey.  
    
    \item The presentation and talk part of the class added more skills into my knowledge. 
    
    \item I believe another thing that benefits me a lot on this class in how to find and search for a conference and for a paper. I wish though we had a chance to work on how to submit a paper.
    
    \item The experimental design and evaluation also was a good topics to know about.  
    
    \item Overall, I really enjoyed this class and its contents and materials.
    \section {The least significant learning experiences}
    \item Things I wish we had more time to learn about are as follow:  
    \item I wish we had more time and materials to learn about the bootstrapping as I we can a lot on them. 
    \item Although the statistical part is very important but I lost my attention when we got to that part of the lecture. I know I will have to go back and learn how to work with statistical once I got to this part with my paper.  
    \item I'm still not really sure about the Hypothesis and the theoretical, experimental evidence. I think more examples need to be added in order to clarify the idea behind them. examples on when and how to implement them. 
    \item Overall, I don't think there are a lot of information that aren't significant because I really enjoyed and benefit from everything on this class. 

    
    \item You can download this file from github from the below link: \url{https://github.com/aabumouzah/Journal-10}
\end{itemize}


\end{document}
